Testing bootstrap processes

### 2024-07-30 test_boot_short_2.Rmd
Able to knit

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-10))
  for (b in 1:B) {
    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
    # (H-1) strata at random
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in unique(df_sample[,3])){
      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
      sample_b <- rbind(sample_b, truc)
      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 5)
}
```

>>>>

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-100))
  for (b in 1:B) {
    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
    # (H-1) strata at random
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in unique(df_sample[,3])){
      truc <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
      muche <- mapply(function(RRRRR){df_sample[rownames(df_sample) == RRRRR,]}, truc)
      sample_b <- rbind(sample_b, t(muche))
      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 5)
}
```
